\thetitle

### 2013-06-19 tfpie/tfpie.tex
my part of sec 3

To begin with, we introduce the notion of a \emph{class definition},
which can be thought of at first as a structure definition in that
it defines a new class of compound data.  A class is defined using the
{\tt define-class} form:
\begin{verbatim}
    (define-class posn (fields x y))
\end{verbatim}
An \emph{object} is a value that is a member of this class of data,
which can be constructed with the {\tt new} keyword, a class name, and
the appropriate number of arguments for the fields of the object:
\begin{verbatim}
    (new posn 3 4)
\end{verbatim}
An object understands some set of \emph{messages}.  Simple
structure-like objects understand messages for accessing their fields
and message are sent by using the {\tt send} keyword, followed by an object,
a message name, and some number of arguments:
\begin{verbatim}
    (send (new posn 3 4) x) ;=> 3
    (send (new posn 3 4) y) ;=> 4
\end{verbatim}
The {\tt send} notation is simple, but syntactically heavy.  Once
students are comfortable with the {\tt send} form, we introduce a
shorthand to make it more convenient by writing {\tt (x . m)} for {\tt
  (send x m)}.  The \emph{dot notation} can be nested, so {\tt (x . m
  . n)} is shorthand for {\tt (send (send x m) n)}.  (The approach of
introducing a simple, uniform syntax and later introducing a
convenient shorthand that would have been confusing to start with
follows the approach of introducing {\tt cons} and later {\tt list}
and {\tt quote} in the first semester.)

It is possible to endow objects with functionality by defining \emph{methods},
which extend the set of messages an object understands.  A method definition
follows the same syntax as a function definition, but is located inside of a
class definition.  Here is a more complete development of the {\tt posn} class
that includes a couple of methods:
\begin{verbatim}
    ;; A Posn is a (new posn Number Number),
    ;; which represents a point on the Cartesian plane
    (define-class posn (fields x y)

>>>>

To begin with, we introduce the notion of a \emph{class definition},
which can be thought of at first as a structure definition in that
it defines a new class of compound data.  A class is defined using the
{\tt define-class} form:
\begin{verbatim}
    (define-class posn (fields x y))
\end{verbatim}
This is similar to the {\tt define-struct} form of the first semester,
used as follows:
\begin{verbatim}
    (define-struct posn (x y))
\end{verbatim}

An \emph{object} is a value that is a member of this class of data,
which can be constructed with the {\tt new} keyword, a class name, and
the appropriate number of arguments for the fields of the object:
\begin{verbatim}
    (new posn 3 4)
\end{verbatim}
An object understands some set of \emph{messages}.  Simple
structure-like objects understand messages for accessing their fields
and message are sent by using the {\tt send} keyword, followed by an object,
a message name, and some number of arguments:
\begin{verbatim}
    (send (new posn 3 4) x) ;=> 3
    (send (new posn 3 4) y) ;=> 4
\end{verbatim}
The {\tt send} notation is simple, but syntactically heavy.  Once
students are comfortable with {\tt send}, we introduce 
shorthand to make it more convenient, writing {\tt (x . m)} for {\tt
  (send x m)}.  The \emph{dot notation} can be nested, so {\tt (x . m
  . n)} is shorthand for {\tt (send (send x m) n)}.  (The approach of
introducing a simple, uniform syntax and later introducing a
convenient shorthand that would have been confusing to start with
follows the approach of first introducing {\tt cons} and then later {\tt list}
and {\tt quote} in the first semester.)

It is possible to endow objects with functionality by defining \emph{methods},
which extend the set of messages an object understands.  A method definition
follows the same syntax as a function definition, but is located inside of a
class definition.  Here is a more complete development of the {\tt posn} class
with two methods:
\begin{verbatim}
    ;; A Posn is a (new posn Number Number),
    ;; which represents a point on the Cartesian plane
    (define-class posn (fields x y)
